---
title: "The Capital of Latin America: Miami"
author: "Daniel Montoya"
date: "October 13, 2021"
output: html_document
---

```{r setup, include=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Interactive Map of Miami-Dade County

\centerMiami is colloquially known as the Capital of Latin America because of the large number of residents who are from or are descendants of residents of South America, Central America, and/or the Caribbean. Miami often conjures images of Calle 8, cafecitos, and Spanglish and depends heavily on these regions for the city's tourism and finance sectors. Using the decennial Census data from 2010, this interactive map demonstrates the percent of total population of a given census block that identify as Hispanic or Latino. The map is interactive and allows the viewer to explore the expansive and sprawling Miami-Dade County to observe demographic changes and dynamics across the geography. The map is color-coded so as to symbolize the Colombian (or Venezuelan or Ecuadorian) flag and the pop-ups are colored in a Midnight Blue in homage to the UNASUR (Union of South American Nations) and CELAC (Community of Latin American and Caribbean States) flags.\center


```{r, include=FALSE, warning=FALSE}

library(leaflet)
library(sf)
library(tidyverse)
library(tidycensus)
library(ggthemes)
library(ggspatial)
library(htmlwidgets)
library(tidytransit)

vars2010 <- load_variables(2010, "sf1")

Miami_HL <- get_decennial(geography = "block",
                          state = "FL", county = "Miami-Dade",
                          year = 2010,
                          output = "wide",
                          variables = c(tot_pop = 'P008001',
                                        hl_pop = 'P009003'),
                          geometry = TRUE)

Miami_HL <- Miami_HL %>%
  mutate(pct_HL = hl_pop / tot_pop) %>%
  filter(tot_pop > 0)

FL_state_plane <- "+proj=tmerc +lat_0=24.33333333333333 +lon_0=-81 +k=0.999941177 +x_0=200000.0001016002 +y_0=0 +ellps=GRS80 +datum=NAD83 +to_meter=0.3048006096012192 +no_defs"

FL_HL_palette <- colorNumeric(c("yellow1", "blue3", "red2"), Miami_HL$pct_HL)

HL_map1 <- leaflet(Miami_HL) %>%
  addProviderTiles("Stamen.TonerLite") %>%
  addPolygons(stroke = FALSE, fillOpacity = 0.7,
    color = ~FL_HL_palette(pct_HL)) %>%
  addLegend("bottomright", pal = FL_HL_palette, values = ~pct_HL,
    title = "Percent of population<br/>identifying as Hispanic or Latino",
    labFormat = labelFormat(suffix = "%",
                            transform = function(x) 100 * x),
    opacity = 1)

HL_map2 <- leaflet(Miami_HL) %>%
  addProviderTiles("Stamen.TonerLite") %>%
  addPolygons(color = ~FL_HL_palette(pct_HL), stroke = FALSE, fillOpacity = 0.7,
              highlightOptions = highlightOptions(fillColor = "midnightblue", fillOpacity = 0.9),
              label = "This is a label",
              popup = "This is a popup") %>%
    addLegend("bottomright", pal = FL_HL_palette, values = ~pct_HL,
    title = "Percent of population<br/>identifying as Hispanic and Latino",
    labFormat = labelFormat(suffix = "%",
                            transform = function(x) 100 * x),
    opacity = 1)

HL_map3 <- leaflet(Miami_HL) %>%
  addProviderTiles("Stamen.TonerLite") %>%
  addPolygons(color = ~FL_HL_palette(pct_HL), stroke = FALSE, fillOpacity = 0.7,
              highlightOptions = highlightOptions(fillColor = "midnightblue", fillOpacity = 0.9),
              label = Miami_HL$NAME,
              popup = paste("Total population: ", Miami_HL$tot_pop, "<br/>",
                            "Hispanic or Latino identifying population: ", Miami_HL$hl_pop, " (", 
                            round(Miami_HL$pct_HL * 100, 1), "%)", sep = "")) %>%
    addLegend("bottomright", pal = FL_HL_palette, values = ~pct_HL,
    title = "Percent of total population<br/>identifying as Hispanic or Latino",
    labFormat = labelFormat(suffix = "%",
                            transform = function(x) 100 * x),
    opacity = 1)

```


```{r map, echo = FALSE, warning=FALSE, message=FALSE, fig.align="center"}

HL_map3

saveWidget(HL_map3, file="interactive_miami_hl.html")

```





